---
title: Generate atmospheric profile from gridded concentration data
author: James C. Womack
output: html_document
---

Set path to data file.

> **NOTE**: The `.csv.gz` file must be decompressed before use, e.g. using
>
> ```
> gunzip --keep HorizontalSliceGrid_2015-08-21T063000_CONCENTRATION.csv.gz
> ```
> 
> which will produce the decompressed `.csv` file, ready for use.
>
> This is necessary, despite `readr::read_csv()` being able to decompress files 
> as needed.
>
> This notebook relies on skipping lines using the `skip` argument to
> `readr::read_csv()`. When using larger values of `skip` to read data from
> later in the file, `readr::read_csv()` produces an error:
> 
> ```
> Error: The size of the connection buffer (131072) was not large enough
to fit a complete line:
>   * Increase it by setting `Sys.setenv("VROOM_CONNECTION_SIZE")`
> ```
> 
> This appears to only occur where the input file is compressed (`.csv.gz`).
> For non-compressed input files (`.csv`), the error does not occur. This 
> [Stack Overflow Q&A](https://stackoverflow.com/questions/68628271/partially-read-really-large-csv-gz-in-r-using-vroom)
> describes a similar issue and suggests that random access from `.csv.gz` files
> may not be possible.

```{r}
# load all necessary packages

library(dplyr)
library(mgcv)
library(broom)
```

```{r}
# set file path to concentration data - NOTE: this will need editing to suit your needs

grid_csv <- fs::path_abs(
  "HorizontalSliceGrid_2015-08-21T063000_CONCENTRATION.csv"
)
```

# Read a single grid of concentration data (slice height 0.0 m)

```{r}
n_rows <- 100
n_skip_lines <- 8

single_grid_concs_tbl <- readr::read_csv(
  file = grid_csv,
  # don't interpret first row as row names
  col_names = FALSE,
  # columns contain floating point data by default
  col_types = readr::cols(.default = readr::col_double()),
  # skip last column (empty due to trailing comma)
  col_select = !tidyselect::last_col(),
  # specify number of rows of data to read
  n_max = n_rows,
  # start reading after skipping lines to "SLICE HEIGHT" heading
  skip = n_skip_lines
  )

print(single_grid_concs_tbl, n = 5)
```

Convert tibble to matrix

```{r}
single_grid_concs_mat <- single_grid_concs_tbl |> as.matrix() |> unname()

print(
  sprintf(
    "grid_concs dimensions: %s",
    paste0(dim(single_grid_concs_mat), collapse = "x")
  )
)
print(
  sprintf(
    "grid_concs object size: %s",
    format(object.size(single_grid_concs_mat), units = "auto", standard = "IEC")
  )
)
```

# Read all grids of concentration data

```{r}
lines <- readr::read_lines(grid_csv)
```

Find positions of tables of data in data file and extract height values

```{r}
# Find line numbers for lines starting with search_pattern
search_pattern <- "^SLICE HEIGHT"
offsets <- stringr::str_which(lines, search_pattern)

# For each line containing search pattern, extract the numeric value of height
# and convert this to a numeric type
extract_pattern <- r"((?<=:,)[0-9]+\.[0-9]+)"
slice_heights <- stringr::str_extract(lines[offsets], extract_pattern) |>
  as.numeric()
```

Function for extracting a single grid of data from a CSV file, documented using
roxygen2, as described in the [R packages book](https://r-pkgs.org/man.html)

```{r}
#' Extract gridded data from CSV containing multiple table
#'
#' Reads `n_max` rows of CSV data, starting from line `offset`, and converts
#' this to a `matrix`. All data is assumed to be numeric and the returned matrix
#' is of type double.
#'
#' @param file Path to file, connection, or literal data, containing CSV data.
#'  To be passed to [readr::read_csv()] `file` argument
#' @param offset Number of lines to skip in `file` before reading gridded data
#' @param n_rows Number of rows of gridded data to read (default: 100)
#' @param skip_last_col Logical indicating whether last column of gridded data
#'  should be ignored. This is useful if the rows of gridded data have a
#'  trailing comma (default: TRUE)
#' @returns A double matrix containing gridded data, with `n_rows` rows and
#'  number of columns determined by the shape of the input data.
get_slice_as_matrix <- function(
  file,
  offset,
  n_rows = 100,
  skip_last_col = TRUE) {
  tbl <- readr::read_csv(
    file = file,
    col_names = FALSE,
    col_types = readr::cols(.default = readr::col_double()),
    n_max = n_rows,
    skip = offset
  )
  if (skip_last_col) {
    tbl <- tbl |> dplyr::select(!tidyselect::last_col())
  }
  mat <- tbl |> as.matrix() |> unname()
  return(mat)
}
```

Create list of matrices for tables of gridded data at each offset (slice height value).

```{r}
mats <- lapply(
  X = offsets,
  FUN = function(x) {
    get_slice_as_matrix(
      grid_csv,
      x,
      n_rows = 100,
      skip_last_col = TRUE
    )
  }
)
```

Create a tibble containing one matrix of gridded data per slice height and sort by slice height (in the input CSV, the 1m slice is after all other slices)

```{r}
grid_concs_tbl <- tibble::tibble(
  slice_height = slice_heights,
  conc_grid = mats
) |> dplyr::arrange(slice_height)

print(grid_concs_tbl, n = 5)
```


```{r}
# slice_height is a double, so check approximate equality
grid_at_1m <- (
  grid_concs_tbl |>
    dplyr::filter(dplyr::near(slice_height, 1.0)) |>
    dplyr::pull(conc_grid)
)[[1]]
grid_at_2m <- (
  grid_concs_tbl |>
    dplyr::filter(dplyr::near(slice_height, 2.0)) |>
    dplyr::pull(conc_grid)
)[[1]]
grid_at_3m <- (
  grid_concs_tbl |>
    dplyr::filter(dplyr::near(slice_height, 3.0)) |>
    dplyr::pull(conc_grid)
)[[1]]

max_abs_diff_1m_2m <- max(abs(grid_at_1m - grid_at_2m))
max_abs_diff_1m_3m <- max(abs(grid_at_1m - grid_at_3m))

print(sprintf("Max. abs. diff (1m, 2m): %e", max_abs_diff_1m_2m))
print(sprintf("Max. abs. diff (1m, 3m): %e", max_abs_diff_1m_3m))
```

# Calculate summed concentrations at each slice height

```{r}
grid_concs_tbl <- grid_concs_tbl |>
  dplyr::mutate(summed_conc = purrr::map_dbl(conc_grid, sum)) |>
  dplyr::mutate(summed_conc = signif(summed_conc * 1000, digits = 4))

print(grid_concs_tbl, n = 5)
plot(grid_concs_tbl$slice_height, grid_concs_tbl$summed_conc)
```

# Exponentially extend concentration data down to value of 0 or to altitude of 278 m

# These commented-out blocks of code can be ignored, they were experiments in using different methods to extend the data past 100 m, such as a nonlinear general additive model, rather than the method of exponential decay that was finally chosen

#```{r}
# plot concentration profile to see shape - linear version
#grid_concs_tbl2 <- grid_concs_tbl %>% select(, -conc_grid)
# create linear model and extract model fitted values
#y_lin <- grid_concs_tbl2$summed_conc
#f_lin <- grid_concs_tbl2$slice_height
#linear_mod_test <- lm(y_lin ~ f_lin)
#linear_test_vec <- linear_mod_test[5]
#test_vec2 <- linear_test_vec$fitted.values
#grid_concs_tbl2$linear <- test_vec2
#plot model against data
#plot(grid_concs_tbl2$slice_height, grid_concs_tbl2$summed_conc)
#lines(grid_concs_tbl2$slice_height, grid_concs_tbl2$linear, col="red")
#```

#```{r}
# test prediction of later values up to 278 metres - linear version
#altitude_extended <- data.frame(f_lin = seq(102, 278, by=2))
#predicted_concs_linear <- predict(linear_mod_test, newdata=altitude_extended)
#beyond_concs_tbl <- tibble(slice_height = seq(102, 278, by=2), summed_conc = predicted_concs_linear)
#grid_concs_tbl3 <- grid_concs_tbl2 %>% select(, -linear)
#extended_concs_tbl <- grid_concs_tbl3 %>% bind_rows(beyond_concs_tbl)
#extended_concs_tbl$summed_conc[extended_concs_tbl$summed_conc<0] <-0
#plot(extended_concs_tbl$slice_height, extended_concs_tbl$summed_conc)
#```

```{r}
# try exponential decay past 100m
grid_concs_tbl2 <- grid_concs_tbl %>% select(, -conc_grid)


decay_tbl <- data.frame(x_decay = c(1, 450))
lambda <- -(log(1e-20/grid_concs_tbl2$summed_conc[101]))/450
decay_x_seq <- seq(1, 450, by=1)

decay_func <- function(x){
  grid_concs_tbl2$summed_conc[101]*exp(-lambda*x)
}

decay_values <- decay_x_seq %>% decay_func
decay_ext_tbl <- tibble(slice_height = seq(102, 1000, by=2), summed_conc = decay_values)
plot(decay_ext_tbl$slice_height, decay_ext_tbl$summed_conc)

```

```{r}
# append decay to first 100 m of profile - exponential decay
extended_concs_tbl <- grid_concs_tbl2 %>% bind_rows(decay_ext_tbl)
extended_concs_tbl$summed_conc[extended_concs_tbl$summed_conc<0] <- 0
extended_concs_tbl$summed_conc[extended_concs_tbl$summed_conc==0] <- 1e-20

#plot to see shape

plot(extended_concs_tbl$slice_height, extended_concs_tbl$summed_conc)
```

#```{r}
# plot concentration profile to see shape - non-linear GAM
#grid_concs_tbl3 <- grid_concs_tbl %>% select(, -conc_grid)
#grid_concs_tbl3 <- subset(grid_concs_tbl3, grid_concs_tbl3$slice_height > 8) # optional line in ase of disjoint in profile
#y_gam <- grid_concs_tbl3$summed_conc
#f_gam <- grid_concs_tbl3$slice_height
#gam_test <- gam(y_gam ~ s(f_gam), method = "REML")
#gam_test_vec <- predict(gam_test, type = "response")
#grid_concs_tbl3$gam <- gam_test_vec
#plot(gam_test, residuals=TRUE, pch=1)
#```

#```{r}
# test prediction of later values up to 1000 metres - non-linear GAM
# configured to replace original data with general additive model fit instead of appending gam-predicted values to the end of original data
# do this only for atmospheres where the gam is a good fit, otherwise swap the commented lines for their counterparts
# or use the exponential decay model found above instead

#altitude_extended <- data.frame(f_gam = seq(102, 1000, by=2))
#predicted_concs_gam <- predict(gam_test, newdata=altitude_extended)
#beyond_concs_tbl <- tibble(slice_height = seq(102, 1000, by=2), gam = predicted_concs_gam)
#grid_concs_tbl4 <- grid_concs_tbl %>% select(, -conc_grid)
#grid_concs_tbl4 <- grid_concs_tbl3 %>% select(, -summed_conc)
#extended_concs_tbl2 <- grid_concs_tbl4 %>% bind_rows(beyond_concs_tbl)

#extended_concs_tbl2$summed_conc[extended_concs_tbl2$summed_conc<0] <- 0
#extended_concs_tbl2$summed_conc[extended_concs_tbl2$summed_conc==0] <- 1e-20

#extended_concs_tbl2$gam[extended_concs_tbl2$gam<0] <- 0
#extended_concs_tbl2$gam[extended_concs_tbl2$gam==0] <- 1e-20
#plot(extended_concs_tbl2$slice_height, extended_concs_tbl2$gam)
#```

Output atmospheric profile to file

Function for creating strings of formatted numbers from a numeric array, 
documented using roxygen2, as described in the [R packages book](https://r-pkgs.org/man.html).

```{r}
#' Make a string containing numbers
#'
#' @description
#' Extract a sequence of numbers from `numbers` and create a string
#' containing the numbers. The numbers in the string are formatted using
#' `format_spec`, and separated by `collapse`. The `n` numbers are extracted
#' from index `start` in the `numbers` array. If there are fewer than `n`
#' numbers in the array from `start` to the end of the array, the output string
#' will contain only numbers up to the end of the array.
#'
#' @param numbers array of numbers (e.g. atomic vector or list)
#' @param start integer start index for values to extract from `numbers`
#' @param n integer number of values to extract from `numbers`
#' @param format_spec format specification string for each number in output,
#'   (to be passed to [sprintf()])
#' @param collapse character string separating numbers in output (to be passed to
#'   [paste0()])
#' @returns A character string containing formatted values from `numbers`
string_of_numbers <- function(
  numbers,
  start,
  n,
  n_max,
  format_spec,
  collapse
) {
  end <- min(start + n - 1, length(numbers))
  string <- paste0(
      sprintf(
        format_spec,
        numbers[seq(start, end)]
      ),
      collapse = collapse
    )
  return(string)
}
```

Assemble lines to output to atmospheric profile file - choose which one to use!

```{r}
# exponential decay model

n_per_line <- 5
format_spec <- "%10.3e"
collapse <- " "
lines_to_output <- seq(1, nrow(extended_concs_tbl), n_per_line) |>
  purrr::map(
    function(n) {
      string_of_numbers(
        numbers = extended_concs_tbl[["summed_conc"]],
        start = n,
        n = n_per_line,
        n_max = nrow(extended_concs_tbl),
        format_spec = format_spec,
        collapse = collapse
      )
    }
  )
```

#```{r}
# non-linear general additive model

#n_per_line <- 5
#format_spec <- "%10.3e"
#collapse <- " "
#lines_to_output2 <- seq(1, nrow(extended_concs_tbl2), n_per_line) |>
#  purrr::map(
#    function(n) {
#      string_of_numbers(
#        numbers = extended_concs_tbl2[["gam"]],
#        # numbers = extended_concs_tbl2[["summed_conc"]],
#        start = n,
#        n = n_per_line,
#        n_max = nrow(extended_concs_tbl2),
#        format_spec = format_spec,
#        collapse = collapse
#      )
#    }
#  )
#```

Create output directory

```{r}
output_dir_path <- fs::dir_create(fs::path_wd("output"))
```

Output lines to text file - Choose Correct option for exponential decay or non-linear model extension of profile

```{r}
# exponential decay model

lines_to_output |> readr::write_lines(
  file = fs::path_join(c(output_dir_path, "60min_final.txt"))
)
```

#```{r}
# non-linear general additive model
#
#lines_to_output2 |> readr::write_lines(
#  file = fs::path_join(c(output_dir_path, "atmospheric_profileV5_15min.txt"))
#)
#```